-

### 2023-01-17 DRAFT_homogeneous_impact_areas.Rmd
doc: Fix eval=F and similar

*Author and date:* Anders Kolstad

@@

## References

@@

The path must be conditional

@@

```{r}
st_crs(infra)$input
```

@@

@@

```{r, warning=F}
infra_trd_ll <- sf::st_transform(infra_trd, 4326)
```

@@

```{r}
myBB_ll <- sf::st_bbox(infra_trd_ll)
```

### Get OSM highways

@@

### Discretize

@@

```{r, fig.cap="Infrastrcture indeks over Trondheim, comparing the continous scale with the ordinal four-step scale. Major roads are in white."}
tmap_arrange(map_trd,
             map_trd_reclassed,
             ncol=1)
```

I tweaked the thresholds for the bins so that most of the forest next to Trondheim (to the left in the map) was in the second lowest class.
This looks pretty good to me.
It depicts a gradient in human presence from high within the build zone, to *no to very low* in the forests and mountains to the west.
Note that there is still considerable human activity also there in the form of outdoor recreation and even forestry.

### Aggregate

@@

```{r}
infra_trd_reclassed_agg <- st_warp(infra_trd_reclassed, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra_trd_reclassed), 
                                   use_gdal = TRUE,
                                   method = "average")
```

@@

Each cell is no the average of the aggregated cells, and hence the value is continous again.
Let's make it discrete.

@@

## Aggregate the entire map to 1x1 km

```{r}
# runtime about 30 sec
infra_agg <- st_warp(infra, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra), 
                                   use_gdal = TRUE,
                                   method = "average")
```

## Discretize the entire map

@@

## Vectorize

@@

```{r}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

Let's plot this now.
First.
lets crop it to reduce computation time.

@@

```{r, eval=F}
saveRDS(infra_agg_discrete_vect_trd, "P:/41201785_okologisk_tilstand_2022_2023/data/infrastrukturindeks/homogeneous_impact_areas.rds")
```

>>>>

*Author and date:*

Anders Kolstad

@@

### References

@@

The path must be conditional:

@@

Print the coordinate reference system:
```{r}
st_crs(infra)$input
```

@@

#### Get OSM highways

@@

```{r, warning=F, eval=F}
infra_trd_ll <- sf::st_transform(infra_trd, 4326)
```

@@

```{r, eval=F}
myBB_ll <- sf::st_bbox(infra_trd_ll)
```

@@

#### Discretize

@@

```{r, fig.cap="Infrastructure indeks over Trondheim, comparing the continous scale with the ordinal four-step scale. Major roads are in white."}
tmap_arrange(map_trd,
             map_trd_reclassed,
             ncol=1)
```

I tweaked the thresholds for the bins so that most of the forest next to Trondheim (to the left in the map) was in the second lowest class.
This looks pretty good to me.
It depicts a gradient in human presence from high within the buildt zone, to *no to very low* in the forests and mountains to the west.
Note that there is still considerable human activity also there in the form of outdoor recreation and even forestry.

#### Aggregate

@@

```{r, warning=F, message=F}
infra_trd_reclassed_agg <- st_warp(infra_trd_reclassed, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra_trd_reclassed), 
                                   use_gdal = TRUE,
                                   method = "average")
```

@@

Each cell is now the average of the aggregated cells, and hence the value is continuous again.
Let's make it discrete.

@@

### Aggregate the entire map to 1x1 km

```{r, eval=F}
# runtime about 30 sec
infra_agg <- st_warp(infra, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra), 
                                   use_gdal = TRUE,
                                   method = "average")
saveRDS(infra_agg, "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

```{r, echo=F}
infra_agg <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

### Discretize the entire map

@@

### Vectorize

@@

```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

Let's plot this now.
First, lets crop it to reduce computation time.

@@

```{r, eval=F}
saveRDS(infra_agg_discrete_vect, "P:/41201785_okologisk_tilstand_2022_2023/data/infrastrukturindeks/homogeneous_impact_areas.rds")
```
